Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity

### 2025-08-30 poster.tex
update poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2025 PhysioNet/CinC Challenge Poster
% Chagas ECG Screening - Team Revenger
% 
% Based on baposter template by T. Reveyrand
% Original template by Brian Amberg (baposter@brian-amberg.de)
% Downloaded from: http://www.LaTeXTemplates.com
% License: CC BY-NC-SA 3.0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage{textcomp}
\usepackage{hyperref}

@@

% Color definitions (reusing 2024 poster color scheme)
\definecolor{bordercol}{RGB}{40,40,40} % Border color of content boxes
\definecolor{headercol1}{RGB}{186,215,230} % Background color for the header in the content boxes (left side)
\definecolor{headercol2}{RGB}{120,120,120} % Background color for the header in the content boxes (right side)
\definecolor{headerfontcol}{RGB}{0,0,0} % Text color for the header text in the content boxes
\definecolor{boxcolor}{RGB}{210,235,250} % Background color for the content in the content boxes

\definecolor{jdhblue}{RGB}{2,93,186}
\definecolor{zkblue}{RGB}{88,135,175}
\definecolor{zkbackground}{RGB}{230,232,234}

@@

\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=zkbackground,
headershape=roundedright, % Specify the rounded corner in the content box headers
headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain
}
%
%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR NAME
%----------------------------------------------------------------------------------------
%
% TODO: Add logos when available - current paths may not exist
% \IfFileExists{images/logo_cau_science.png}{\includegraphics[scale=0.401]{images/logo_cau_science.png}}{CAU Logo}
{{\bf TODO: CAU Logo}} % University/lab logo placeholder
{
{\bf \fontsize{18pt}{18pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity}
} % Poster title
{\vspace{0.3em} \smaller Hao WEN$^1$, Jingsu KANG$^2$  \\  % Author names

$^1${\it College of Science, China Agricultural University}\\
$^2${\it Tianjin Medical University} \\
\vspace{0.2cm}
{\Large \bf{The George B. Moody PhysioNet Challenge 2025} $\cdot$ \bf{Team Revenger}}
}
% \IfFileExists{logo_tmu.jpeg}{\includegraphics[scale=0.101]{logo_tmu.jpeg}}{TMU Logo}
{{\bf TODO: TMU Logo}} % University logo placeholder

@@

\headerbox{Introduction \& Challenge Context}{name=introduction, column=0, row=0, span=3}{

@@

\vspace{0.3cm}
\begin{center}
\begin{tabular}{rlll}
\toprule
Dataset & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Chagas \%} & Label source \\
\midrule
SaMi-Trop   & 1,631     & 100.0 \%    & expert-confirmed \\
CODE-15\%   & 345,779   & 1.8 \%      & self-reported \\
PTB-XL      & 21,799    & 0.0 \%      & N/A (non-endemic) \\
\bottomrule
\end{tabular}
\end{center}
\vspace{0.3cm}

@@

Hierarchical supervision encoding source reliability through stratified label smoothing:

\vspace{0.2cm}
{\bf Formula:} $\tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1}$
\vspace{0.2cm}

Where smoothing factor $\varepsilon$ depends on reliability:
\begin{itemize}
\item SaMi positives: $\varepsilon = 0.0$ (max trust)
\item CODE-15\% samples: $\varepsilon = 0.6$ (uncertainty)  
\item PTB-XL negatives: $\varepsilon = 0.2$ (mild regularization)
\end{itemize}

@@

\headerbox{Model Architecture}{name=architecture, column=0, row=2, span=2, below=data}{

{\bf Enhanced 1D ResNet with SE Modules \& Global Pooling}

\begin{center}
\resizebox{0.95\linewidth}{!}{%
\begin{tikzpicture}[
    line width=0.75pt,
    >={Latex[length=3mm]},
    node distance=6.4mm,
    every node/.style={inner sep=2pt},
    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=blue!10},
    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
                  align=center, fill=orange!12},
    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
               align=center, fill=green!12},
    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=cyan!10},
    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=purple!10},
    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                align=center, fill=red!10},
    arrow/.style={-{Latex[length=3mm]}, thick},
]

% Main architecture path
\node[stem] (input) {Input \\ (12$\times$L)};
\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};
\node[block, below=of stem] (bottleneck) {$4 \times$ Bottleneck Block \\ ks: 1--15--1, stride: 1--4--1 \\ Ch: $512 \to 768 \to 1024 \to 1280$};
\node[se, below=of bottleneck] (gse) {Global SE \\ reduction=8};
\node[pool, below=of gse] (gap) {Global MaxPool};
\node[head, below=of gap] (mlp) {MLP Head \\ (1280 $\rightarrow$ C=2)};
\node[output, below=of mlp] (out) {Output Logits};

% Arrows
\draw[arrow] (input) -- (stem);
\draw[arrow] (stem) -- (bottleneck);
\draw[arrow] (bottleneck) -- (gse);
\draw[arrow] (gse) -- (gap);
\draw[arrow] (gap) -- (mlp);
\draw[arrow] (mlp) -- (out);

\end{tikzpicture}
}
\end{center}

\begin{itemize}
\item {\bf Bottleneck blocks}: 1$\times$1–15$\times$1 convolutions with expansion factor 4, stride 4 downsampling
\item {\bf Global SE}: Channel attention with reduction ratio 8 for temporal feature recalibration  
\item {\bf Variable-length inputs}: Global max pooling enables inference on ECGs of any duration
\end{itemize}

@@

\headerbox{Training \& Optimization}{name=training, column=2, row=2, span=1, below=supervision}{

{\bf Asymmetric Loss \& Optimization Setup}

\begin{itemize}
\item {\bf Asymmetric Loss}: $L = -y(1-p)^{\gamma_{+}} \log(p) - (1-y)(p_m)^{\gamma_{-}} \log(1-p_m)$
\item Parameters: $(\gamma_{+},\gamma_{-})=(1,4)$, margin $\delta=0.05$
\item {\bf Optimizer}: AdamW with OneCycle scheduler
\item {\bf Learning rate}: $1 \times 10^{-4}$ initial, $6 \times 10^{-4}$ peak
\item {\bf Training}: 30 epochs, batch size 128, weight decay $1 \times 10^{-2}$
\item {\bf Input}: 4,096 samples (uniform crop/center trim)
\item {\bf Early stopping}: Challenge score on 20\% internal hold-out
\end{itemize}

@@

\headerbox{Acknowledgements}{name=acknowledgements, column=0, row=5, span=3, below=discussion}{

We thank Professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers. We acknowledge the PhysioNet Challenge organizers and the contributing datasets.

@@

\headerbox{References}{name=references, column=0, row=6, span=3, below=acknowledgements}{

\begin{thebibliography}{9}
\bibitem{goldberger2000} Goldberger AL, et al. PhysioBank, PhysioToolkit, and PhysioNet. {\it Circulation} 2000;101(23):e215-e220.
\bibitem{ribeiro2020} Ribeiro AH, et al. Automatic diagnosis of the 12-lead ECG using a deep neural network. {\it Nat Commun} 2020;11:1760.
\bibitem{hu2018} Hu J, et al. Squeeze-and-Excitation Networks. {\it CVPR} 2018:7132-7141.
\bibitem{ridnik2021} Ridnik T, et al. Asymmetric Loss For Multi-Label Classification. {\it ICCV} 2021:82-91.
\bibitem{yun2019} Yun S, et al. CutMix: Regularization Strategy to Train Strong Classifiers. {\it ICCV} 2019:6023-6032.
\bibitem{chawla2002} Chawla NV, et al. SMOTE: Synthetic Minority Oversampling Technique. {\it JAIR} 2002;16:321-357.
\end{thebibliography}

@@

\headerbox{}{name=foottext, column=0, span=3, below=references, textborder=none, headerborder=none, boxheaderheight=0pt}{
\hfill \small \textit{Code, configs, etc. are available at https://github.com/wenh06/cinc2025, and is based on https://github.com/DeepPSP/torch\_ecg.}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NIWeek 2014 Poster by T. Reveyrand
% www.microwave.fr
% http://www.microwave.fr/LaTeX.html
% ---------------------------------------
%
% Original template created by:
% Brian Amberg (baposter@brian-amberg.de)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage{textcomp}
\usepackage{eso-pic}
\usepackage{enumitem}
\usepackage{hyperref}

\setlist[itemize]{
  itemsep=1.5pt,
  topsep=3pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=1em,
  labelsep=0.4em
}

\setlength{\abovedisplayskip}{3pt plus 1pt minus 1pt}
\setlength{\belowdisplayskip}{3pt plus 1pt minus 1pt}

@@

\definecolor{bordercol}{RGB}{40,40,40} % Border color of content boxes
\definecolor{headercol1}{RGB}{186,215,230} % Background color for the header in the content boxes (left side)
\definecolor{headercol2}{RGB}{120,120,120} % Background color for the header in the content boxes (right side)
\definecolor{headerfontcol}{RGB}{0,0,0} % Text color for the header text in the content boxes
\definecolor{boxcolor}{RGB}{210,235,250} % Background color for the content in the content boxes

\definecolor{jdhblue}{RGB}{2,93,186}

\definecolor{zkblue}{RGB}{88,135,175}
\definecolor{zkbackground}{RGB}{230,232,234}

% \usetikzlibrary{shapes, arrows, external, decorations.pathmorphing, backgrounds, positioning, fit, petri, calc, hobby, cd}

@@

% \background{ % Set the background to an image (background.pdf)
% \begin{tikzpicture}[remember picture,overlay]
% \draw (current page.north west)+(-2em,2em) node[anchor=north west]
% {\includegraphics[height=1.1\textheight]{images/baposter_background.pdf}};
% \end{tikzpicture}
% }

% add conference banner
\AddToShipoutPictureFG*{%
  \AtPageLowerLeft{%
    \hspace{0.82em}
    \raisebox{0.2ex}{\includegraphics[width=0.16\textwidth]{cinc2025-banner.png}}
  }
}

\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
% boxColorOne=boxcolor, % Background color for the content in the content boxes
boxColorOne=zkbackground,
headershape=roundedright, % Specify the rounded corner in the content box headers
headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
textborder=rectangle,
% background=user,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain
}
%
%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR NAME
%----------------------------------------------------------------------------------------
%
{\includegraphics[scale=0.401]{logo_cau_science.png}} % University/lab logo
{
{\bf \fontsize{19pt}{19pt} \selectfont Reliability-Aware Hierarchical Learning for Chagas Detection from ECG under Expert Label Scarcity}
} % Poster title
{\vspace{0.3em} \smaller Hao WEN$^1$, Jingsu KANG$^2$  \\  % Author names

$^1${\it College of Science, China Agricultural University}\qquad
$^2${\it Tianjin Medical University} \\
\vspace{0.2cm}
{\Large \bf{The George B. Moody PhysioNet Challenge 2025}, ~~~\bf{Team Revenger}}
}
{\includegraphics[scale=0.101]{logo_tmu.jpeg}}

\newif\ifcoloredtext
\coloredtexttrue
\newif\ifboxednn
\boxednntrue

@@

\headerbox{Proposed Reliability-Aware Framework}{name=introduction, column=0, row=0, span=3}{

@@

\begin{center}
\begin{tabular}{rlll}
\toprule
Dataset & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Chagas \%} & Label source \\
\midrule
SaMi-Trop   & 1,631     & 100.0 \%    & expert-confirmed \\
CODE-15\%   & 345,779   & 1.8 \%      & self-reported \\
PTB-XL      & 21,799    & 0.0 \%      & N/A (non-endemic) \\
\bottomrule
\end{tabular}
\end{center}

@@

Hierarchical supervision encoding source reliability through stratified label smoothing:
\[
\text{\bf Formula:} ~~ \tilde{\mathbf{y}} = (1 - \varepsilon) \cdot \mathbf{y} + \frac{\varepsilon}{C} \cdot \mathbf{1}
\]
Where smoothing factor $\varepsilon$ depends on reliability:
\begin{itemize}
\item SaMi positives: $\varepsilon = 0.0$ (max trust)
\item CODE-15\% samples: $\varepsilon = 0.6$ (uncertainty)  
\item PTB-XL negatives: $\varepsilon = 0.2$ (mild regularization)
\end{itemize}

@@

\headerbox{Model Architecture}{name=architecture, column=0, row=2, span=1, below=data}{

{\bf Enhanced 1D ResNet with SE Modules}

\begin{center}
\resizebox{1.03\linewidth}{!}{%
  \input{tikz_plots/resnet_nature_comm_bottle_neck}
}
\end{center}

\begin{itemize}
\item {\bf Bottleneck blocks}: 1-15-1 convolutions, expansion factor 4, stride 4 downsampling
\item {\bf Global SE}: Channel attention, reduction ratio 8 for temporal feature recalibration  
\item {\bf Variable-length inputs}: Global MaxPool enables inference on ECGs of any duration
\end{itemize}

@@

\headerbox{Training \& Optimization}{name=training, column=1, row=2, span=1, below=data}{

% {\bf Asymmetric Loss \& Optimization Setup}

\begin{itemize}
\item {\bf Asymmetric Loss}: $L = -y(1-p)^{\gamma_{+}} \log(p) - (1-y)(p_m)^{\gamma_{-}} \log(1-p_m)$
\item Parameters: $(\gamma_{+},\gamma_{-})=(1,4)$, margin $\delta=0.05$
\item {\bf Optimizer}: AdamW
\item {\bf LR Scheduler}: OneCycle
\item {\bf LR}: $1 \times 10^{-4}$ initial, $6 \times 10^{-4}$ peak
\item {\bf Training}: 30 epochs, batch size 128, weight decay $1 \times 10^{-2}$
\item {\bf Input}: 4,096 samples (uniform crop/center trim)
\item {\bf Early stopping}: Challenge score on 20\% internal hold-out subset
\end{itemize}

@@

% \headerbox{Acknowledgements}{name=acknowledgements, column=0, row=5, span=3, below=discussion}{

% We thank Professor {\bf Deren Han} from the School of Mathematical Sciences, Beihang University for providing GPU servers. We acknowledge the PhysioNet Challenge organizers and the contributing datasets.

% }

@@

% \headerbox{References}{name=references, column=0, row=6, span=3, below=acknowledgements}{

% \begin{thebibliography}{9}
% \bibitem{goldberger2000} Goldberger AL, et al. PhysioBank, PhysioToolkit, and PhysioNet. {\it Circulation} 2000;101(23):e215-e220.
% \bibitem{ribeiro2020} Ribeiro AH, et al. Automatic diagnosis of the 12-lead ECG using a deep neural network. {\it Nat Commun} 2020;11:1760.
% \bibitem{hu2018} Hu J, et al. Squeeze-and-Excitation Networks. {\it CVPR} 2018:7132-7141.
% \bibitem{ridnik2021} Ridnik T, et al. Asymmetric Loss For Multi-Label Classification. {\it ICCV} 2021:82-91.
% \bibitem{yun2019} Yun S, et al. CutMix: Regularization Strategy to Train Strong Classifiers. {\it ICCV} 2019:6023-6032.
% \bibitem{chawla2002} Chawla NV, et al. SMOTE: Synthetic Minority Oversampling Technique. {\it JAIR} 2002;16:321-357.
% \end{thebibliography}

% }

@@

\headerbox{}{name=foottext, column=0, span=3, below=future, textborder=none, headerborder=none, boxheaderheight=0pt}{
\hfill \small \textit{Code, configs, etc. are available at https://github.com/wenh06/cinc2025, and is based on https://github.com/DeepPSP/torch\_ecg.}
}
